To be FAIR: Theory Specification Needs an Update

### 2025-06-06 action_letter.Rmd
update 2025-06-06 18:48:11.101405

```{r setup-chunk, include = FALSE}
revise::read_manuscript("manuscript.Rmd")
```

@@

@@

@@

@@

>>>>

```{r setup-chunk, include = FALSE}
library(revise)
revise::read_manuscript("abstract.md")
revise::read_manuscript("manuscript.Rmd")
```

@@

We thank the Reviewer for their thoughtful review and detailed comments. We have sought to address all comments, and feel that doing so has improved the quality of the manuscript.

@@

Thank you for this suggestion; as proposed, we now briefly mention the R-package in the abstract:

`r get_revision("abstractpackage")`

@@

nakagawaPoorHypothesesResearch2024

@@

gonzalezExtrinsicConvergentValidity2021
